---
title: "Simple document"
output: html_document #what output do you want#
---

**Refer back to the lecture website for more details/tools!**

Load in your packages first, R Markdown starts from scratch every time 
```{r}
library(tidyverse)
```

I'm an R Markdown document! Use "Knit" to output everything!

# Section 1
Hashtags create a new section (# Section 1)

**Two asterisks** on either side of text bolds,
_Two underscores_ on either side of text italicizes.

Add an extra blank line in between for a new line
  
Here's a **code chunk** that samples from 
a _normal distribution_:

Three backticks ' before r in squiggly parentheses means this is R code,
which you can run!
```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.
Rounded to 2 digits, `r round(mean(samp), 2)`

In the above example, you can *use backticks '' around "r _something_"* and it
will run that command and output the results as text (in this case, we did _mean(samp)_).

Use _round(mean(samp), 2)_ to round to 2 digits:


# Section 3

This is going to make a plot!

_Option + command + i_ will create an R markdown code chunk (ie three backticks {R}).

```{r ggplot histogram}
plot_df =
  tibble(
    x = rnorm(n = 1000),
    y = 1 + 2 * x + rnorm(n = 1000)
  )

ggplot(plot_df, aes(x = x, y=y)) + geom_point()
```

For R Markdown, you need to load all the packages you need before running R code,
For the above code for example, you need to reload the library(tidyverse) so it
can run tibble and ggplot. **Load your packages in a separate codechunk at the very
beginning of the doc!**

The Render tab (by the Consol and Terminal tabs) shows the percentage breakdown
and organization of the R Markdown chunks.

**Naming your codechunks can help you keep track of them, the names will show up in the Render tab**

**Name your codechunk at the beginning of the codechunk, in the curly brackets after r**

